LDATS Codebase

### 2023-09-17 doc/LDATS_codebase.Rmd

---
title: "Latent Dirichlet Allocation Time Series (LDATS)"
author: "Juniper L. Simonis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LDATScodebase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

To minimize the length of argument lists and facilitate simple default usage
throughout the pipeline, we implement an options/controls list approach, where
each of the main functions (`LDA_TS`, `LDA_set`, and `TS`) has a controls 
list (although `LDA_set` is referenced as `LDA` in the naming scheme)

* `LDA_TS_controls_list()`
* `LDA_controls_list()`
* `TS_controls_list()`

>>>>

---
title: "LDATS Codebase"
author: "Juniper L. Simonis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LDATS Codebase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

To minimize the length of argument lists and facilitate simple default usage
throughout the pipeline, we implement an options/controls list approach, where
each of the main functions (`LDA_TS`, `LDA_set`, and `TS`) and its subfunctions
have a `control` argument that takes a `list` to replace the defaults returned 
by its `_control` function:

* `LDA_TS_control()`
* `LDA_set_control()`
* `TS_control()`
